### 2025-03-24 writing/manuscript.tex
prep for meet 1

>>>>

\begin{figure}[H]
  \centering
  \caption{Performance by Tie Strength and SES}
  \includegraphics[width=0.85\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/tie_combined.png}
  \label{fig:tie_score_ses}
  \caption*{\footnotesize\textit{Note:} This figure shows local polynomial regressions of network math and reading z-scores by social tie strength across socioeconomic status groups with 95\% confidence intervals. Higher SES have steeper positive relationships between tie strength and the average performance those in their network across reading and math scores.}
\end{figure}
